An analysis of Lenin's work: Revolution, war, and fruta

### 2014-02-20 paper/paper.tex
Change name from Wn Analyzer to SynsetAnalyzer.
fix in my surname

\author{Leonardo Lázzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Juan Manuel Pérez,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
}

@@

% *WordnetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
%

>>>>

\author{Leonardo Lazzaro,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Julián Peller,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
Juan Manuel Pérez,\affil{1}{Universidad de Buenos Aires, Buenos Aires, Argentina},
}

@@

% *SynsetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
%
